Two-Dimensional Vesicle Hydrodynamics from Hydrophobic Attraction Potential

### 2021-12-29 doc/reviews/ResponseToReviewer2.tex

\documentclass[11pt]{article}

\usepackage{hyperref}
\usepackage{fullpage}
\usepackage{color}
\usepackage{newtxmath}
\newcommand{\comment}[1]{{\color{blue} #1}}

\begin{document}

\noindent
Dear Prof.~Petia Vlahovska,
\\ \\
\noindent
Thank you for handling the manuscript, and we would like to thank the
reviewer for their positive and constructive comments. The attached
manuscript addresses all the reviewer's comments and the result is what
we believe is a stronger manuscript. An itemized list of the changes
addressing the reviewer's comments are below. Changes to the manuscript
from Reviewers 1, 2, and 3 are colored in \textcolor{red}{red},
\textcolor{green}{green}, and \textcolor{magenta}{magenta},
respectively. \\ \\
\noindent
Sincerely,
\\
\noindent
Szu-Pei, Bryan Quaife, Rolf Ryham, and Yuan-Nan Young

\section*{Response to Reviewer 2}
\comment{
\noindent
The authors are introducing a novel numerical approach to study vesicles
under flow conditions in two dimensions. The vesicle is modelled as a
collection of amphiphilic Janus particles (JP) interacting with each
other through a hydrophobic attraction potential (HAP) and a short-range
repulsion force to avoid the overlap between particles. Both the
mobility of the particles and the HAP are recast in the form of an
integral equation of the second kind and solved numerically. The authors
presented some results on the deformation and dynamic of a single
vesicle and a pair of vesicles in different type of external flows.
\\ \\
\noindent
The originality of this work stems from coupling the HAP and Stokes
equations through a boundary integral formulation which I personally
find quite interesting. However, numerical models for vesicles and other
class of soft particles in 2D and 3D are already well established in the
literature. Disregarding the 2D nature of the model, I am not fully
convinced on how this approach outperforms the existing models either in
computational performance or in new applications. The authors should
make an extra effort to highlight this. Another weakness of this model,
if I understood correctly, is that the area of the vesicle is not
conserved beyond the small deformation limit. To the best of my
knowledge, a 2D vesicle should fulfill both constant area and perimeter
constraints. This means that the range of application of the model is
limited to the small deformation limits when used to mimic vesicles
under flow. Finally, this paper lacks a thorough validation of the
numerical results with the existing data in the literature and/or an
original application/result describing a physical phenomenon not covered
by the previous literature. This work is suitable for publication in
this journal but a major revision is needed. Below additional minor
comments to be addressed.}
\begin{itemize}
  \item Change 1
  \begin{quotation}
    \noindent
    Can put verbatim change in this environment.
  \end{quotation}
\end{itemize}

\noindent
\comment{The abbreviation HAP is not defined in the text. I guess it stands for hydrophobic attraction potential.
}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{$u$ is used for both the velocity and the solutions of the
Laplace equation. Please use another variable for the scalar function
$u$.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{$\rho$ used in the HAP is not the same as the one used in the
mobility boundary integral equation. One is a decay length of the
attraction potential, while the second is the Euclidean distance between
two JPs.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{$\nu$ is used on multiple instances, sometimes as a normal
vector (see line 97 for example), and other times as some scalar
function (see line 203).}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{What is the bending modulus here? I guess that it is not a
direct input parameter in this model but rather a quantity that can be
deduced from other input parameters. If I am right then, what are these
parameters? And could you tune them if needed to simulate the effect of
the membrane stiffness? This can be important in some applications such
as rigidity-based microfluidic sorting devices.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{To compare the results with the existing literature, I would
suggest introducing the capillary number for vesicles as defined in
\url{https://doi.org/10.1016/j.crhy.2009.10.001}.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{For both examples with the linear shear flow and the Poiseuille
flow, the area of the vesicle is not conserved and the relative error
with respect to the stress-free area increases with the increase of the
external stresses. It can reach roughly 7-8\% for the higher shear rate
in the shear flow example. This is quite significant. Do you have a way
to reduce this error to below 1\%? Note that in other numerical models
for vesicles (e.g.~\url{https://doi.org/10.1016/j.jcp.2008.11.036}),
both constant area and perimeter constraints are fulfilled even when the
vesicle is more deformed than the cases reported here.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{In some interesting applications, the fluid encapsulated by the
bilayer membrane has a viscosity which is different from the suspending
fluid. How difficult it is to add this feature to your model?}
\begin{itemize}
  \item Change 1 
\end{itemize}

\end{document}

### 2021-12-29 doc/reviews/ResponseToReviewer3.tex

\documentclass[11pt]{article}

\usepackage{hyperref}
\usepackage{fullpage}
\usepackage{color}
\usepackage{newtxmath}
\newcommand{\comment}[1]{{\color{blue} #1}}

\begin{document}

\noindent
Dear Prof.~Petia Vlahovska,
\\ \\
\noindent
Thank you for handling the manuscript, and we would like to thank the
reviewer for their positive and constructive comments. The attached
manuscript addresses all the reviewer's comments and the result is what
we believe is a stronger manuscript. An itemized list of the changes
addressing the reviewer's comments are below. Changes to the manuscript
from Reviewers 1, 2, and 3 are colored in \textcolor{red}{red},
\textcolor{green}{green}, and \textcolor{magenta}{magenta},
respectively. \\ \\
\noindent
Sincerely,
\\
\noindent
Szu-Pei, Bryan Quaife, Rolf Ryham, and Yuan-Nan Young

\section*{Response to Reviewer 3}
\comment{\noindent
The manuscript extends the authors’ previous work on modeling
amphiphilic particles in a viscous solvent to modeling amphiphilic Janus
particles suspended in a viscous background flow. The authors adopted
the GMRES iterative method to solve the screened Laplace equation for
hydrophobic attraction. They investigated the inter-monolayer friction
of vesicles formed by amphiphilic Janus particles and corresponding
membrane ruptures in viscous flows, and simulated the spatial migration
dynamics of a vesicle in a parabolic flow and also the hydrodynamics of
two vesicles in shear and extensional flows.
\\ \\
\noindent
This manuscript presents a systematic study of the hydrodynamics of
vesicles formed by amphiphilic Janus particles in viscous flows. It
provides quantitative analysis of the inter-monolayer friction, membrane
permeability and the migration dynamics of soft suspended vesicles. The
topic on hydrodynamics of complex fluids is interesting, and this
research fits the scope of Journal of Fluid Mechanics. Here, I am in a
favor of its publication at some points if the authors can address the
following concerns in the revised manuscript.
}
\begin{itemize}
  \item Change 1
  \begin{quotation}
    \noindent
    Can put verbatim change in this environment.
  \end{quotation}
\end{itemize}

\noindent
\comment{In section 2.2, the authors defined a repulsion force with an
empirical formula to prevent particle collisions. However, there is no
benchmark test to show that this artificial repulsion force can generate
correct hydrodynamic lubrication. The authors are suggested to justify
and validate the use of the Imposed Forces with comparison to well-known
lubrication forces between particles.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{Fig.~3 plots the time evolution of the reduced area in (a) and
the excess length of the bilayer structure in (b). Both show obvious
oscillations with multiple frequencies, which are not as smooth as the
inset of (c) showing one dominant frequency. The authors are suggested
to explain the source of multiple frequencies generated in the time
evolution of $A$ and $\Delta$.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{Fig.~6 illustrates the migration process of a JP vesicle in a
parabolic flow, where the moving velocity is 8 nm/ns and the time frame
is 0 to 12 $\mu$s. Given the length scale R = 20 nm, the migration
distance should be $1000 \times R$. However, in the figure, it shows a
migration distance about 4x R. The authors are suggested to double-check
their model parameterization.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{In Fig.~10, the significant discontinuities in streamlines
across the surface of vesicles are observed, while in most other cases
the streamlines are smooth across the interface of vesicles. The authors
are suggested to describe such discontinuity and provide the
explanation.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{Minor: I read some grammatical errors in the manuscript that
should be corrected, i.e., ``replicate well-know vesicle hydrodynamics
$\ldots$" on page 2, ``$\ldots$ a baseline JP vesicles $\ldots$" on page
8, ``circular vesicles has a Laplace pressure $\ldots$" at Eq.~(4.7).
The authors are suggested to have a thorough read of the manuscript.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\end{document}

### 2021-12-29 doc/reviews/ResponseToReviewer1.tex

\noindent
\comment{Section 2.2: for clarity, define the variable u as the
hydrophobic attraction potential in the first paragraph.}

\noindent
\comment{The equations of the continuous time evolution of the particle
positions and orientations should be written in Section 2 to close the
problem.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{I think the time-discretization Section 2.3 should go at the
end of Section 3 since this is the one devoted to the numerical
discretization of the governing equations. Also, the sentence ``particle
collisions are avoided even when using a relatively large time step" is
very vague.  What do you mean by ``relatively large time step"? Compared
to what time scale?}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{Section 3: the acronym HAP is not defined in the text.}
\begin{itemize}
  \item Thank you for noticing this oversight. The definition of HAP has
    been added at its first occurrence in Section 3.1. 
  \item This change is in \textcolor{green} since it was also pointed
    out by Reviewer 2.
\end{itemize}

\noindent
\comment{Equation 3.1: use parenthesis to show that the normal
derivative only applies to the Laplace’s Green function $K_0$ and not
the density $\sigma$.}
\begin{itemize}
  \item Parenthesis have been added to equation (3.1)

  \item Equations (3.2) and (3.11) had the same notational issue, and
    they have both been corrected.
\end{itemize}

\noindent
\comment{For clarity, use contraction products ``$\cdot$" when a second
order tensor multiplies a vector to avoid confusion (e.g.~${\bf S} \cdot
{\bf F}$ instead of ${\bf SF}$) in eqs.~(3.4), (3.5), (3.7) and so on
$\ldots$}
\begin{itemize}
  \item This notation has been adjusted throughout Section 3.
\end{itemize}

\noindent
\comment{In practice, how do you compute the derivatives $d\sigma /ds$,
$dv_i/ds$ and $dv_i/d\boldsymbol{\nu}$ in (3.13)?}
\begin{itemize}
  \item Since the only derivatives that are required are functions
    defined only on the boundary of the Janus particles, they are
    computed with spectrally-accurate Fourier differentiation.

  \item We have added the following sentence to the start of Section 3
    \begin{quotation}
      All derivatives are computed with spectrally-accurate Fourier
      differentiation.
    \end{quotation}
\end{itemize}

### 2021-12-29 doc/reviews/ResponseToReviewer3.tex

\noindent
\comment{In section 2.2, the authors defined a repulsion force with an
empirical formula to prevent particle collisions. However, there is no
benchmark test to show that this artificial repulsion force can generate
correct hydrodynamic lubrication. The authors are suggested to justify
and validate the use of the Imposed Forces with comparison to well-known
lubrication forces between particles.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{Fig.~3 plots the time evolution of the reduced area in (a) and
the excess length of the bilayer structure in (b). Both show obvious
oscillations with multiple frequencies, which are not as smooth as the
inset of (c) showing one dominant frequency. The authors are suggested
to explain the source of multiple frequencies generated in the time
evolution of $A$ and $\Delta$.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{Fig.~6 illustrates the migration process of a JP vesicle in a
parabolic flow, where the moving velocity is 8 nm/ns and the time frame
is 0 to 12 $\mu$s. Given the length scale R = 20 nm, the migration
distance should be $1000 \times R$. However, in the figure, it shows a
migration distance about $4 \times R$. The authors are suggested to
double-check their model parameterization.}
\begin{itemize}
  \item Change 1 
\end{itemize}

@@

\noindent
\comment{In Fig.~10, the significant discontinuities in streamlines
across the surface of vesicles are observed, while in most other cases
the streamlines are smooth across the interface of vesicles. The authors
are suggested to describe such discontinuity and provide the
explanation.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{Minor: I read some grammatical errors in the manuscript that
should be corrected, i.e., ``replicate well-know vesicle hydrodynamics
$\ldots$" on page 2, ``$\ldots$ a baseline JP vesicles $\ldots$" on page
8, ``circular vesicles has a Laplace pressure $\ldots$" at Eq.~(4.7).
The authors are suggested to have a thorough read of the manuscript.}
\begin{itemize}
  \item The typo with ``well-know" is corrected, but colored in red
    since it was pointed out by Reviewer 1.

  \item The manuscript now reads
    \begin{quotation}
      $\ldots$ a baseline JP vesicle $\ldots$
    \end{quotation}

  \item The typo with ``has" instead of ``have" is corrected, but
    colored in red since it was pointed out by Reviewer 1.

  \item We have read through the manuscript and made grammatical
    changes.

\end{itemize}
